---
title: "Data Pipeline"
output: html_document
---

This document allows running your full analysis, in concise code: the nitty-gritty details should be handled by your functions, not in this document.


# Gather
This step of the analysis is where you gather the data files used in your analysis.  
```{r gather}
source("0_general_functions.R")
source("1_gather/gather_functions.R")

## Replace {GATHER_OBJECTS} with the R objects you created in this phase
save({GATHER_OBJECTS}, file = "1_gather/gathered.Rdata")

# save session info
session_to_file("1_gather/gather_session_info.txt")

```

# Transform
This is where you alter your data to prepare for analysis.
```{r transform}
source("0_general_functions.R")
load("1_gather/gathered.Rdata")

source("2_transform/transform_functions.R")

save({TRANSFORM_OBJECTS}, file = "2_transform/transformed.Rdata")

# save session info
session_to_file("2_transform/transform_session_info.txt")

```

# Analyze
This is where you actually calculate descriptives and fit models.  All model objects should be saved so that you can present them in different possible ways in the "present" step.
```{r analyze}
source("0_general_functions.R")
load("2_transform/transformed.Rdata")

source("3_analyze/analyze_functions.R")

save({ANALYZE_OBJECTS}, file = "3_analyze/analyzed.Rdata")


# save session info
session_to_file("3_analyze/analyze_session_info.txt")

```

# Present
This is where you generate reports.  This should be done by calling the "render" function on your Rmd or Rnw file, which is in the "04_present/" folder.
```{r present}
source("0_general_functions.R")
## Code for calling render() functions on any Rmd files (all stored in '04_present/'
## folder)


```

